Quick, Draw! Image Classification

### 2018-12-07 report/draft.tex
tried to structure our report more

%
% PPUA 5262 Final
%
\documentclass[12pt]{article}

@@

We generate a series of hypotheses to inform our analysis.

@@

We start off with hypothesis that we learnt from theoretical literature. We
then perform several experiments to test the validity of these hypothesis and
report out our findings. Some of our hypothesis is as follows:

1) Fully connected neural network will struggle to get reasonable accuracy.
In contrast CNN’s should perform better and faster than a Fully connected
neural network.

2) Training a deep neural network with limited data will result in
overfitting. Conversely, adding more data to a deep neural network is an
effective way to manage variance.

3) Imbalance class prediction can be improved using data augmentation.

4) Increasing the number of categories will cause a significant drop in the
performance of the neural network. Increasing the overall data points for the
network to be trained on should help.

@@

Google originally collected the data from users by explicitly asking them to
draw objects like forks, hotdogs, etc. The original dataset is 70 GB in size
but Google also provides a simplified version of the dataset- consisting only
of the final images. We used these '.npy' files to train all of our models.
These numpy bitmap files consist of more than 100,000 rows each and 784
features, since they are basically $28 \times 28$ images. Samples of these
images are shown in Figure \ref{fig:quickImages}. The subset of this
dataset sampled varies from experiment to experiment. More details can be
found in the experiments mentioned below.

@@

\subsection{Hypothesis 1}

Hypothesis 1: Fully connected neural network will struggle to get reasonable
accuracy. In contrast CNN’s should perform better and faster than a Fully
connected neural network.

@@

\subsection{Hypothesis 2}

Hypothesis 2: Training a deep neural network with limited data will result in overfitting. Conversely, adding more data to a deep neural network is an effective way to manage variance.

With us reaching an optimal model for the dataset, we decided to study the effect of reduction in the sampled dataset and its relationship with overfitting.

\subsection{Hypothesis 3}

We tried to show the importance of having equal partitions of data to train a machine learning model. Imbalanced classes can make a model biased toward the majority class.

@@

>>>>

%
% DS 5220 Final
%
\documentclass[12pt]{article}

@@

We generate hypotheses based on expectations related to model performance. We
then conduct preprocessing steps on our data.

\subsection{Overview of Statistical Modeling Techniques}

We use human classification, fully connected neural networks,
and a Convolutional Neural Network (CNN). We discuss the CNN in
more detail than was covered in class so an overview is provided
here.

\subsubsection{Convolutional Neural Network (CNN)}

TODO: explain how we used a CNN or anything else not covered in class

@@

We have generated the following hypotheses based on theoretical
expectations:

\subsubsection{Addressing model component of performance}

\begin{align*}
  H1_a: &\text{Fully Connected Neural Network will struggle} \\
  &\text{ to get reasonable accuracy.} \\
  H2_a: &\text{CNN should perform better than fully} \\
  &\text{connected neural network.} \\
\end{align*}

\subsubsection{Addressing data component of performance}
\begin{align*}
  H3_a: &\text{Small amounts of data will lead to overfitting.} \\
  H4_a: &\text{Imbalanced class prediction can be improved}\\
  &\text{using data augmentation.} \\
  H5_a: &\text{Addition of a category to the trained model will} \\
  &\text{reduce the performance of the model.} \\
  H6_a: &\text{Adding more training data will improve the} \\
  &\text{performance of the model.} \\
\end{align*}

TODO: more context would be helpful here, maybe some citations

@@

Google originally collected the data from users by explicitly asking users to
draw objects like forks, hotdogs, etc. The original dataset is 70 GB in size
but Google also provides a simplified version of the dataset- consisting only
of the final images. We used these '.npy' files to train all of our models.
These numpy bitmap files consist of more than 100,000 rows each and 784
features, since they are basically $28 \times 28$ images. Samples of these
images are shown in Figure \ref{fig:quickImages}. The subset of this
dataset sampled varies from experiment to experiment. More details can be
found in the experiments mentioned below.

@@

We report our results by examining the validity of each hypothesis.

\subsection{Addressing model component of performance}

@@

\subsection{Addressing data component of performance}

ok

@@

Talk about our final slide and tie the hypotheses together
